Self Regulation Ontology Retest Analyses

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
wrapped up draft analyses

@@

>>>>

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')

ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

```{r}
tmp %>%
  group_by(contrast) %>%
  summarise(mean_icc = mean(icc),
            sd_icc = sd(icc))
```
